Dantzig Selector \\ Applied on mm-Wave MIMO: \\ Part I. Expected Error Analysis

### 2019-08-30 dantzig_selector/depr_presentation/1_slide.tex
Code: Rearrange methods into lambda expressions

\Subsubtitle{May 30, 2019}
\Subsubtitle{Graduate Instute of Commnication Engineering, \\ National Taiwan University}
\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Organization}
{
\I Problem Configuration Proposed Method

@@

\I Concentration Inequality of \m {\M{P}}

\I Restricted Isometry of \m {\M{P}}

@@

\I References
}
\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Background}
{
\I Multiple-input-multiple-output (MIMO) wireless communication is expected to be the next-generation r\'egime

@@

\I If the sparsity is exploited, can few observations suffice to estimate the channel?
}
\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Compressive Sensing}
{
\I Such case of channel estimation is facilitated by advances of so-called compressed sensing (CS)

\I CS addresses the situation that the number of model parameters \m {N_p} the number of measurements \m {N_m}.

@@

\I Work on CS reveals that few observations of the signal may be sufficient for us to resonstruct the signal when it is sparse.

\I In the advent, Cand\`es and Tao (2006) proposes the Dantzig Selector (DS) as an possible answer.
}
\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
\Frametitle {Notation}

{\tfx
\starttable[|l|l|l|] \HL
\NC Expression \VL Meaning or Definition \VL More Explanation \SR \HL
\NC \m {f \SB {x}} \VL square brackets \VL only for arguments \AR \HL
\NC \m {\V {a}} \VL vector \VL  \AR \HL
\NC \m {\M {A}} \VL matrix \VL  \AR \HL
\NC \m {\V {a} \DB {n}} \VL \m {n}-th component of \m {\V {a}} \VL  \AR \HL
\NC \m {\M {A} \DB {m,n}} \VL \m {m,n}-th entry of \m {\M {A}} \VL  \AR \HL
\NC \m {\MB {V}_{\MB {K}} \SB {N}} \VL Hilbert space \m {\MB {K}^N} over \m {\MB {K}} \VL \m {\MB {K} =\MB {R}} or \m {\MB {C}} \AR \HL
\NC \m {\VNm {\V {a}} _p} \VL \m {\ell_p}-norm of \m {\V {a}} \VL \m {p >0} \AR \HL
\NC \m {\MB {M}_{\MB {K}} \SB {M,N}} \VL collection of \m {M} by \m {N} matrices \VL  \AR \HL
\stoptable
}
% % % % % % % % % % % % % % % % % % % % % % % % % %

>>>>

\Subsubtitle{May 30, 2019}
\Subsubtitle{Graduate Instute of Commnication Engineering, \\ National Taiwan University}

\page [yes]
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Organization}
{
\I Problem Configuration

\I Proposed Method

@@

\I Concentration Inequality and Restricted Isometry of \m {\M{P}}

@@

\I References
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Background}
{
\I Multiple-input-multiple-output (MIMO) wireless communication is expected to be the next-generation r\'egime

@@

\I If the sparsity is exploited, can few observations suffice to estimate the channel?
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Compressive Sensing}
{
\I Such case of channel estimation is facilitated by advances of so-called compressed sensing (CS)

\I CS addresses the situation that the number of model parameters \m {N_p \gg} the number of measurements \m {N_m}.

@@

\I Much work on CS reveals that few observations of the signal may be sufficient for us to reconstruct the signal when it is sparse.

\I In the advent, Cand\`es and Tao (2006) propose the Dantzig Selector (DS) as a possible answer.
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frametitle {Notation}
{
{\tfx
\starttable[|l|l|l|] \HL
\NC Expression \VL Meaning or Definition \VL More Explanation \SR \HL
\NC \m {f \SB {x}} \VL square brackets \VL only for arguments \AR \HL
\NC \m {\V {a}} \VL vector \VL  \AR \HL
\NC \m {\M {A}} \VL matrix \VL  \AR \HL
\NC \m {\V {a} \DB {n}} \VL \m {n}-th component of \m {\V {a}} \VL  \AR \HL
\NC \m {\M {A} \DB {m,n}} \VL \m {m,n}-th entry of \m {\M {A}} \VL  \AR \HL
\NC \m {\MB {V}_{\MB {K}} \SB {N}} \VL Hilbert space \m {\MB {K}^N} over \m {\MB {K}} \VL \m {\MB {K} =\MB {R}} or \m {\MB {C}} \AR \HL
\NC \m {\VNm {\V {a}} _p} \VL \m {\ell_p}-norm of \m {\V {a}} \VL \m {p >0} \AR \HL
\NC \m {\MB {M}_{\MB {K}} \SB {M,N}} \VL collection of \m {M} by \m {N} matrices \VL \m {\MB {K} =\MB {R}} or \m {\MB {C}} \AR \HL
\stoptable
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
